Cancer Applications of Choropleth Maps, and the Potential of Cartograms and Alternative Map Displays

### 2019-12-17 review_article.Rmd
Inset map completed

| Fig. | Atlas | Statistic | Data source | 
|:----:|:-------------|:----------------------|:----------------|  
|1a | The Environment and Health Atlas of England and Wales | relative risk for women developing lung cancer in England and Wales in 2010 [@EnvEnglandWales2]| [ Office for National Statistics (ONS) (England) and from the Welsh Cancer Intelligence and Surveillance Unit (WCISU) ](http://www.envhealthatlas.co.uk/homepage/)|
|1b | Globocan 2018: Estimated Cancer Incidence, Mortality and Prevalence Worldwide | age standardized incidence rates (per 100,000) for all invasive cancers for both men and women, aggregated at a national level for 2018 [@Globocan]| [World Health Organization's International Agency for Research on Cancer](https://www.iarc.fr/). |
|1c | Atlas of Cancer in Queensland | the relative incidence ratio of lung cancer in males in the state of QLD within Australia based on data from 1998 to 2007, Queensland Cancer Council[@QLDcancerAtlas] | [Queensland Cancer Registry](https://cancerqld.org.au/research/cancer-registries/queensland-cancer-registry/) |
|1d | Bowel Cancer Australia Atlas | the percentage of Australian males between 50 - 54 years of age diagnosed with bowel cancer in 2016 in Australia [@Bowel]. |  [Bowel Cancer Australia](https://www.bowelcanceraustralia.org/)|
|1e | United States Cancer Statistics: An Interactive Cancer Statistics Website | the incidence rate per 100,000, of all cancer types for men and women in the United States in 2016, aggregated at the state level [@USInteractive].|  *[Centers for Disease Control and Prevention](https://www.cdc.gov/)*, with data from state cancer registries. | 
|1f | Map of Cancer Mortality Rates in Spain | side by side maps of relative risk of lung cancer for men vs women for 2004 to 2008 [@cancerSpain].| [Map of cancer mortality rates in Spain](https://elpais.com/elpais/2014/10/06/media/1412612722_141933.html)|
|1g | Atlas of Childhood Cancer in Ontario | the incidence rate of childhood cancers per 100,000 (by census division) for children aged 0-14, in Ontario from 1995 to 2004 [@OntarioPediatric]. | [The Pediatric Oncology Group of Ontario Networked Information System](https://www.pogo.ca/research-data/pogonis-childhood-cancer-database/data-requests/)|

>>>>

|Fig.| Atlas | Statistic | Data source | 
|:---:|:------------|:----------------------|:----------------|  
|1a | The Environment and Health Atlas of England and Wales | relative risk for women developing lung cancer in England and Wales in 2010 [@EnvEnglandWales2]| [ Office for National Statistics (ONS) (England) and from the Welsh Cancer Intelligence and Surveillance Unit (WCISU) ](http://www.envhealthatlas.co.uk/homepage/)|
|1b | Globocan 2018: Estimated Cancer Incidence, Mortality and Prevalence Worldwide | age standardized incidence rates (per 100,000) for all invasive cancers for both men and women, aggregated at a national level for 2018 [@Globocan]| [World Health Organization's International Agency for Research on Cancer](https://www.iarc.fr/). |
|1c | Atlas of Cancer in Queensland | the relative incidence ratio of lung cancer in males in the state of QLD within Australia based on data from 1998 to 2007, Queensland Cancer Council[@QLDcancerAtlas] | [Queensland Cancer Registry](https://cancerqld.org.au/research/cancer-registries/queensland-cancer-registry/) |
|1d | Bowel Cancer Australia Atlas | the percentage of Australian males between 50 - 54 years of age diagnosed with bowel cancer in 2016 in Australia [@Bowel]. |  [Bowel Cancer Australia](https://www.bowelcanceraustralia.org/)|
|1e | United States Cancer Statistics: An Interactive Cancer Statistics Website | the incidence rate per 100,000, of all cancer types for men and women in the United States in 2016, aggregated at the state level [@USInteractive].|  *[Centers for Disease Control and Prevention](https://www.cdc.gov/)*, with data from state cancer registries. | 
|1f | Map of Cancer Mortality Rates in Spain | side by side maps of relative risk of lung cancer for men vs women for 2004 to 2008 [@cancerSpain].| [Map of cancer mortality rates in Spain](https://elpais.com/elpais/2014/10/06/media/1412612722_141933.html)|
|1g | Atlas of Childhood Cancer in Ontario | the incidence rate of childhood cancers per 100,000 (by census division) for children aged 0-14, in Ontario from 1995 to 2004 [@OntarioPediatric]. | [The Pediatric Oncology Group of Ontario Networked Information System](https://www.pogo.ca/research-data/pogonis-childhood-cancer-database/data-requests/)|
